---
title: "SurvivalData"
author: "Manik Garg"
date: "28/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("ggplot2")
theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))
```

## TCGA data
```{r}
rawExpressionData = read.table("~/Downloads/TCGA_RNASeqRawCounts.txt", sep = " ", header = TRUE, quote = "")
```

```{r}
rawExpressionDataSubset = rawExpressionData[-c(60484:60488), 2:ncol(rawExpressionData)]
rownames(rawExpressionDataSubset) = gsub("\"", "", rawExpressionData$X..[-c(60484:60488)])
```

```{r}
rownames(rawExpressionDataSubset) = gsub("[[:punct:]].*","", rownames(rawExpressionDataSubset))
```

Load the clinical data
```{r}
clinicalDataSampleId = read.table("~/Downloads/Clinical_details.xlsx - Sheet2.tsv", sep = "\t", header = TRUE, quote = "")
```

```{r}
#Make sure that the clinical data is in the same order as expression data
rownames(clinicalDataSampleId) = paste("X.", make.names(clinicalDataSampleId$sampleID), ".", sep = "")
```

Available tumor tissue sites = 
table(clinicalDataSampleId$tumor_tissue_site)

                                                                                         
                                                                                      34 
                                                                      Distant Metastasis 
                                                                                      65 
                                                                           Primary Tumor 
                                                                                      88 
Regional Cutaneous or Subcutaneous Tissue (includes satellite and in-transit metastasis) 
                                                                                      75 
                                                                     Regional Lymph Node 
                                                                                     219 
                                                                                     
```{r}
cam_121_genes = read.table("~/Downloads/matched-gene-list.tsv", sep = "\t", quote = "", header = TRUE)
rawExpressionDataSubsetTissue = rawExpressionDataSubset[rownames(rawExpressionDataSubset) %in% cam_121_genes$mappedGeneId, colnames(rawExpressionDataSubset) %in% rownames(clinicalDataSampleId)[clinicalDataSampleId$tumor_tissue_site %in% c("Regional Cutaneous or Subcutaneous Tissue (includes satellite and in-transit metastasis)", "Primary Tumor")]]
```

```{r}
clinicalData = clinicalDataSampleId[rownames(clinicalDataSampleId)%in%colnames(rawExpressionDataSubsetTissue), ]
#Make sure that the clinical data is in the same order as the sample expression data
seIdx = match(colnames(rawExpressionDataSubsetTissue), rownames(clinicalData))
clinicalData = clinicalData[seIdx, ]
```

Apply vst normalization: Create dds object
```{r}
library("DESeq2")
dds <- DESeqDataSetFromMatrix(countData = rawExpressionDataSubsetTissue,
                              colData = clinicalData,
                              design = ~ 1)
dds
```
Apply vst normalization: Actually do the normalization
```{r}
#BiocManager::install("vsn")
library("vsn")
vsd = varianceStabilizingTransformation(dds, fitType="local")
meanSdPlot(assay(vsd))
```

```{r}
vstNormalizedExpressionData = assay(vsd)
betaCoeff = read.table("~/Downloads/betaCoeff.tsv", sep = "\t", header = TRUE, quote = "")
#Make sure that the beta coefficient data is in the same order as samples in the expression data
betaCoeffSubset = betaCoeff[rownames(vstNormalizedExpressionData), ]
seIdx = match(rownames(vstNormalizedExpressionData), rownames(betaCoeffSubset))
betaCoeffSubset = betaCoeffSubset[seIdx, ]
reducedSignature = apply(vstNormalizedExpressionData*betaCoeffSubset$EventMet_Yes_vs_No, 2, sum)
stand.fun = function(x){(x-mean(x,na.rm=TRUE))/sd(x,na.rm=TRUE)}
clinicalData$Signature = stand.fun(reducedSignature) 
clinicalData$Group = ifelse(clinicalData$Signature >= as.numeric(quantile(clinicalData$Signature,0.33)), "High", "Low")
#clinicalData$Group = ifelse(clinicalData$Signature >= -0.44, "High", "Low")
```

```{r}
#write.table(clinicalData[, c("Signature", "Group")], "Cam_121_TCGA_LN.tsv", sep = "\t", col.names = TRUE, row.names = TRUE)
```


```{r}
quantile(clinicalData$Signature,0.33)
```

```{r}
library('survival')
clinicalData$survival_d_rc = Surv(time  = (clinicalData$X_OS)/365.25,
                              event = as.numeric(clinicalData$X_OS_IND))
```

Perform the univariate analysis
```{r}
summary(coxph(survival_d_rc ~ Signature, 
      data = clinicalData))
```
```{r}
summary(coxph(survival_d_rc ~ Group, 
      data = clinicalData))
```
```{r}
summary(coxph(survival_d_rc ~ Group+gender+age_at_initial_pathologic_diagnosis+pathologic_stage, 
      data = clinicalData))
```
```{r}
library(survminer)
fit <- survfit( survival_d_rc ~ Group, 
      data = clinicalData )
ggsurv <- ggsurvplot(fit, data = clinicalData, 
                     palette = "npg",                              # jco palette
                     pval = TRUE, pval.coord = c(0.5, 0.25),        # Add p-value
                     risk.table = TRUE,                            # Add risk table
                     font.main = c(10),
   font.x = 10,
   font.y = 10,
   font.tickslab = 10,
   font.legend = 10,
   fontsize = 10,
   pval.size=3.5)

ggsurv
#ggarrange(ggsurv$plot, ggsurv$table, heights = c(2, 0.7),
#          ncol = 1, nrow = 2, align = "v")
ggsave("Cam_121_TCGA_Ln_OS.png",plot = ggsurv$plot, device = "png", width = 16, units = "cm")
```
```{r}

```

```{r}
tcga_surv = data.frame()
fit = coef(summary(coxph(survival_d_rc ~ Signature,data=clinicalData)))
mid  = fit["Signature",c("exp(coef)")]
low  = exp(fit["Signature",c("coef")]-
              qnorm(.975)*fit["Signature",c("se(coef)")])                   
high = exp(fit["Signature",c("coef")]+
              qnorm(.975)*fit["Signature",c("se(coef)")])  
pval = fit["Signature",c("Pr(>|z|)")]
tcga_surv["Signature",c("HR","low","high","pval")] = c(mid,low,high,pval)

fit = coef(summary(coxph(survival_d_rc ~ Signature+gender+age_at_initial_pathologic_diagnosis+pathologic_stage,
                         data=clinicalData)))
mid  = fit["Signature",c("exp(coef)")]
low  = exp(fit["Signature",c("coef")]-
              qnorm(.975)*fit["Signature",c("se(coef)")])                   
high = exp(fit["Signature",c("coef")]+
              qnorm(.975)*fit["Signature",c("se(coef)")])  
pval = fit["Signature",c("Pr(>|z|)")]
tcga_surv["Signature+Sex+Age+Stage",c("HR","low","high","pval")] = c(mid,low,high,pval)

fit = coef(summary(coxph(survival_d_rc ~ Signature+gender+age_at_initial_pathologic_diagnosis+breslow_depth_value,
                         data=clinicalData)))
mid  = fit["Signature",c("exp(coef)")]
low  = exp(fit["Signature",c("coef")]-
              qnorm(.975)*fit["Signature",c("se(coef)")])                   
high = exp(fit["Signature",c("coef")]+
              qnorm(.975)*fit["Signature",c("se(coef)")])  
pval = fit["Signature",c("Pr(>|z|)")]
tcga_surv["Signature+Sex+Age+Breslow",c("HR","low","high","pval")] = c(mid,low,high,pval)

tcga_surv$Group = rownames(tcga_surv)
```

```{r}
tcga_surv$Group
```

```{r}
tcga_surv$Group <- factor(tcga_surv$Group, levels = c("Signature+Sex+Age+Breslow", "Signature+Sex+Age+Stage", "Signature"))
g1 <- ggplot(data=tcga_surv,
       aes(x = Group,y = HR, ymin = low, ymax = high, label = #paste("p-value=",formatC(pval,format="e"), sep = "")))+
   paste("p=",round(pval, 4), sep = "")))+
   geom_pointrange()+
   geom_hline(yintercept =1, linetype=2)+
   xlab('')+
   ylab("Hazard Ratio (95% Confidence Interval)")+
   geom_errorbar(aes(ymin=low, ymax=high),width=0.2,cex=1)+ 
   ylim(c(0,4))+
   geom_text(hjust = -.05, vjust=-0.55)+
   coord_flip()+
   theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))
ggsave("FP_Cam_121_TCGA_Skin_OS.png", device = "png", width = 16, units = "cm", )
```
```{r}
ggarrange(ggsurv$plot, g1, heights = c(1, 1),
          ncol = 1, nrow = 2, align = "v", font.label = list(size = 10))
ggsave("Cam_121_TCGA_Skin_OS.png", device = "png", width = 16, units = "cm")
```
```{r}
#amgpData = read.csv("~/Downloads/AMGPts_CAM121.csv")
```

## Leeds data

```{r}
library(survival)
library(survminer)

data = read.table("~/Downloads/LMCdata_Manik12feb2020.txt", sep = "\t", header = TRUE, quote = "")
rownames(data) = data$manik_id
data = data[!(rownames(data) == "4220077"), ]
#data = data[complete.cases(data$ajccstage), ]
data$Signature = - data$negativeScore121
data$Group = factor(ifelse(data$Signature >= as.numeric(quantile(data$Signature,0.33)), "High", "Low"))
survival_Object = Surv(data$msstime, as.numeric(factor(data$died_mm)))
fit = survfit(survival_Object ~ factor(data$Group))

#fit <- survfit(survObj ~ Group, data = data)
ggsurv <- ggsurvplot(fit, data = data, 
                     palette = "npg",                              # jco palette
                     pval = TRUE, pval.coord = c(0.5, 0.25),        # Add p-value
                     risk.table = FALSE,                            # Add risk table
                     font.main = c(10),
   font.x = 10,
   font.y = 10,
   font.tickslab = 10,
   font.legend = 10,
   fontsize = 10,
   pval.size=3.5)

## Forest plot
leeds_surv = read.delim("~/Downloads/ForestPlot_Cam121_Cam70_LMC.txt")
leeds_surv = leeds_surv[1:3, ]
leeds_surv$Group = c("Cam_121", 
"Cam_121+Sex+Age+Breslow+\nUlceration+Mitotic count+\nBRAF+NRAS",
"Cam_121+Sex+Age+Breslow+\nUlceration+Mitotic count+\nBRAF+NRAS+TIL count")
leeds_surv$Group <- factor(leeds_surv$Group, levels = c("Cam_121+Sex+Age+Breslow+\nUlceration+Mitotic count+\nBRAF+NRAS+TIL count", "Cam_121+Sex+Age+Breslow+\nUlceration+Mitotic count+\nBRAF+NRAS", "Cam_121"))

#ggarrange(ggsurv$plot, ggsurv$table, heights = c(2, 0.7),
#          ncol = 1, nrow = 2, align = "v")

g1 <- ggplot(data=leeds_surv,
       aes(x = Group,y = Hazard_Ratio, ymin = Lower_HazardRatio, ymax = Upper_HazardRatio, label = paste("p=",p_value, sep = "")))+
   geom_pointrange()+
   geom_hline(yintercept =1, linetype=2)+
   xlab('')+
   ylab("Hazard Ratio (95% Confidence Interval)")+
   geom_errorbar(aes(ymin=Lower_HazardRatio, ymax=Upper_HazardRatio),width=0.2,cex=1)+ 
   ylim(c(0,4))+
   geom_text(hjust = -.05, vjust=-0.55)+
   coord_flip()+
   theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))

ggarrange(ggsurv$plot, g1, heights = c(1, 1),
          ncol = 1, nrow = 2, align = "v", font.label = list(size = 10))
ggsave("Cam_121_Leeds_Skin_MSS.png", device = "png", width = 16, units = "cm")
```

## Lund's data

```{r}
library(survival)
data = read.table("~/Downloads/Annots_for_Roy.txt",sep="\t",header=T,row.names=1,as.is=T)
time<-data$OS_rfs
outKap<-data$OSbin_rfs
a<-Surv(time,outKap)

#A) RFS: Kaplan-Meier of two groups by median
psig<-data$zscore
Group <- ifelse(psig >= as.numeric(quantile(psig, 0.33)), "High", "Low")
fit = survfit(a~Group)

#fit <- survfit(survObj ~ Group, data = data)
ggsurv <- ggsurvplot(fit, data = data, 
                     palette = "npg",                              # jco palette
                     pval = TRUE, pval.coord = c(0.5, 0.25),        # Add p-value
                     risk.table = FALSE,                            # Add risk table
                     font.main = c(10),
   font.x = 10,
   font.y = 10,
   font.tickslab = 10,
   font.legend = 10,
   fontsize = 10,
   pval.size=3.5)
ggsave("Cam_121_Lund_Skin_PFS.png", device = "png", width = 16, units = "cm")

summary(coxph(a~Group))
```

## Forest plot for 24 genes
```{r}
genes_24_surv = data.frame("HR" = c(1.2153, 1.234568),
                           "low" = c(0.99731, 0.8403361),
                           "high" = c(1.4808, 1.785714),
                           "pval" = c(0.053209, 0.28),
                           "Group" = c("Cam_24+Sex+Age+Stage+\nECOG+treatment+Nclass",
                                       "Cam_24+Sex+Age+Breslow+\nUlceration+Mitotic count+\nBRAF+NRAS+TIL count"),
                           "Cohort" = c("AVAST-M Skin", "LMC"),
                           "Event" = c("PFS", "MSS"))

genes_24_surv$Group <- factor(genes_24_surv$Group, levels = c("Cam_24+Sex+Age+Breslow+\nUlceration+Mitotic count+\nBRAF+NRAS+TIL count", "Cam_24+Sex+Age+Stage+\nECOG+treatment+Nclass"))

g1 <- ggplot(data=genes_24_surv,
       aes(x = Group,y = HR, ymin = low, ymax = high, 
           color = Cohort,
           label = paste("p=",pval, sep = "")))+
   geom_pointrange()+
   geom_hline(yintercept =1, linetype=2)+
   xlab('')+
   ylab("Hazard Ratio (95% Confidence Interval)")+
   geom_errorbar(aes(ymin=low, ymax=high),width=0.1,cex=1)+ 
   ylim(c(0,4))+
   geom_text(hjust = -.05, vjust=-1)+
   scale_color_brewer(type = "qual", palette = "Set2")+
   coord_flip()+
   theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))

g1
ggsave("Cam_24_Skin.png", device = "png", width = 16, height = 8, units = "cm")
```
## AVAST-M data

```{r}


pfs = read.table("~/Downloads/SurvivalResults_Signature_overlap_DASLarray_genes_PFS_Weighted_med_3.txt", sep = "\t", header = TRUE, quote = "")
```

```{r}
tilCount = read.table("./AVAST-M_TILCount.tsv", sep = "\t", header = TRUE, quote = "")
#tilCount$MIAScore = as.factor(tilCount$MIAScore)
tilCount = tilCount[!duplicated(tilCount$R.Seq_sampleID), c("ClarkScore", "Scanned_file.me", "R.Seq_sampleID", "MIAScore")]
rownames(tilCount) = tilCount$R.Seq_sampleID
#cam_121$Sample = rownames(cam_121)
```

```{r}
cam_121 = read.table("./Cam_121_AvastM_Skin.tsv", sep = "\t", header = TRUE, quote = "")
cam_121$Group = as.factor(cam_121$Group)
cam_121$Sample = rownames(cam_121)
```

```{r}
library(DESeq2)
load("./tcSkinEventMetNo_VS_tcSkinEventMetYes_CovariateCorrection.deseq2/de.Rdata")
```

```{r}
#merge the til counts and the signature together
clinicalData = data.frame(colData(dds))
clinicalData = merge(clinicalData, cam_121, by.x = "RNA.Seq.Sample", by.y = "Sample")
rownames(clinicalData) = clinicalData$RNA.Seq.Sample
clinicalData$ClarkScore <- NA
clinicalData$ClarkScore[rownames(tilCount)%in%rownames(clinicalData)]= as.character(tilCount$ClarkScore[rownames(tilCount)%in%rownames(clinicalData)])
clinicalData$ClarkScore = as.factor(clinicalData$ClarkScore)
```

```{r}
# survival outcome 1: "d" for death and "ltrc" for left truncated and right censored
clinicalData$survival_d_ltrc = Surv(time  = as.numeric(difftime(clinicalData$DOE, clinicalData$DDiag))/365.25,
                                    time2 = as.numeric(difftime(clinicalData$DOC, clinicalData$DDiag))/365.25,
                                    event = ifelse(clinicalData$Dead == FALSE, 0, 1))

# survival outcome 2: "rd" for relapse or death, "ltrc" for left truncated and right censored
clinicalData$survival_rd_ltrc = Surv(time  = as.numeric(difftime(clinicalData$DOE, clinicalData$DDiag))/365.25,
                                     time2 = as.numeric(difftime(apply(clinicalData[, c("DOC", "DDistMets")],1,min,na.rm=TRUE), clinicalData$DDiag))/365.25,
                                     event = ifelse((clinicalData$Dead == FALSE & clinicalData$EventMet == "No"), 0, 1))
```

```{r}
summary(coxph(survival_d_ltrc~Signature+Sex+Age+as.numeric(Nclass)+as.character(Stage)+ECOG+treatment+ClarkScore,
             data=clinicalData))
os = read.table("~/Downloads/SurvivalResults_Signature_overlap_DASLarray_genes_OS_Weighted_median_3.txt", sep = "\t", header = TRUE, quote = "")
os = os[7:nrow(os),]
os = rbind(os, c("Signature+Sex+Age+Stage+ECOG+Treatment+Nclass+TILCount", 
                1.612205,
                1.25727,
                2.067,
                0.000167))
os$Group = c("Cam_121", 
             "Cam_121+Sex", 
             "Cam_121+Age", 
             "Cam_121+Stage", 
             "Cam_121+ECOG", 
             "Cam_121+Treatment", 
             "Cam_121+Nclass",
             "Cam_24+Sex+Age+Stage+\nECOG+treatment+Nclass",
             "Cam_24+Sex+Age+Stage+\nECOG+treatment+Nclass+\nTIL count")
os$Event = c("OS")
```
```{r}
summary(coxph(survival_rd_ltrc~Signature+Sex+Age+as.numeric(Nclass)+as.character(Stage)+ECOG+treatment+ClarkScore,
             data=clinicalData))
pfs = read.table("~/Downloads/SurvivalResults_Signature_overlap_DASLarray_genes_PFS_Weighted_med_3.txt", sep = "\t", header = TRUE, quote = "")
pfs = pfs[7:nrow(pfs),]
pfs = rbind(pfs, c("Signature+Sex+Age+Stage+ECOG+Treatment+Nclass+TILCount", 
               1.634809,
                1.2883,
                2.074,
                5.24e-05))
pfs$Group = c("Cam_121", 
             "Cam_121+Sex", 
             "Cam_121+Age", 
             "Cam_121+Stage", 
             "Cam_121+ECOG", 
             "Cam_121+Treatment", 
             "Cam_121+Nclass",
             "Cam_24+Sex+Age+Stage+\nECOG+treatment+Nclass",
             "Cam_24+Sex+Age+Stage+\nECOG+treatment+Nclass+\nTIL count")
pfs$Event = c("PFS")
```
```{r}
df = rbind(os, pfs)
df$Group = as.factor(df$Group)
df$Group = factor(df$Group, levels = rev(levels(df$Group)))
df$Event = as.factor(df$Event)

g1 <- ggplot(data=df[df$Event=="OS", ],
       aes(x = Group,y = as.numeric(Hazard_Ratio), ymin = as.numeric(Lower_HazardRatio), ymax = as.numeric(Upper_HazardRatio), 
           #color = Event,
           label = paste("p=",p_value, sep = "")))+
   geom_pointrange()+
   geom_hline(yintercept =1, linetype=2)+
   xlab('')+
   ylab("Hazard Ratio (95% Confidence Interval)")+
   geom_errorbar(aes(ymin=as.numeric(Lower_HazardRatio), ymax=as.numeric(Upper_HazardRatio)),width=0.1,cex=1)+ 
   geom_text(hjust = -.05, vjust=-1)+
   #scale_y_continuous()+
   ylim(c(0,4))+
   #scale_color_brewer(type = "qual", palette = "Set2")+
   coord_flip()+
   theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))

g2 <- ggplot(data=df[df$Event=="PFS", ],
       aes(x = Group,y = as.numeric(Hazard_Ratio), ymin = as.numeric(Lower_HazardRatio), ymax = as.numeric(Upper_HazardRatio), 
           #color = Event,
           label = paste("p=",p_value, sep = "")))+
   geom_pointrange()+
   geom_hline(yintercept =1, linetype=2)+
   xlab('')+
   ylab("Hazard Ratio (95% Confidence Interval)")+
   geom_errorbar(aes(ymin=as.numeric(Lower_HazardRatio), ymax=as.numeric(Upper_HazardRatio)),width=0.1,cex=1)+ 
   geom_text(hjust = -.05, vjust=-1)+
   #scale_y_continuous()+
   ylim(c(0,4))+
   #scale_color_brewer(type = "qual", palette = "Set2")+
   coord_flip()+
   theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))


g3 <- ggplot(data=df,
       aes(x = Group,y = as.numeric(Hazard_Ratio), ymin = as.numeric(Lower_HazardRatio), ymax = as.numeric(Upper_HazardRatio), 
           color = Event,
           label = paste("p=",p_value, sep = "")))+
    geom_pointrange(position=position_dodge(width=0.5))+
    geom_hline(yintercept =1, linetype=2)+
    xlab('')+
    ylab("Hazard Ratio (95% Confidence Interval)")+
    geom_errorbar(aes(ymin=as.numeric(Lower_HazardRatio), ymax=as.numeric(Upper_HazardRatio)),width=0.1,cex=1, position=position_dodge(width=0.5))+ 
    geom_text(hjust = -.05, vjust=-1.5, position=position_dodge(width=0.5))+
    #scale_y_continuous()+
    ylim(c(0,4))+
    scale_color_brewer(type = "qual", palette = "Set2")+
    coord_flip()+
    theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))
   
#ggarrange(g1, g2, align = "h", ncol = 1, nrow = 2, heights = c(4, 4))
ggsave(plot = g1, filename = "Cam_121_OS.png", device = "png", width = 16, units = "cm")
ggsave(plot = g2, filename = "Cam_121_OS.png", device = "png", width = 16, units = "cm")
ggsave(plot = g3, filename = "Cam_121_OS.png", device = "png", width = 16, height = 16,  units = "cm")
```

```{r}
library(survival)
library(survminer)
library(ggfortify)
fit = survfit(survival_d_ltrc ~ Group, data = clinicalData)
# g1<- autoplot(fit, pval = TRUE)+
#    ylab("Survival")+
#    scale_color_manual(values = c("#E31A1C", "#1F78B4"), name = "Group")+
#    scale_fill_manual(values = c("#E31A1C", "#1F78B4"), name = "Group")

ggsurvplot(fit, data = clinicalData, 
                     surv.median.line = "hv",
                     palette = "npg",                              # jco palette
                     pval = TRUE, pval.coord = c(0.5, 0.25),        # Add p-value
                     risk.table = FALSE,                            # Add risk table
                     font.main = c(10),
   font.x = 10,
   font.y = 10,
   font.tickslab = 10,
   font.legend = 10,
   fontsize = 10,
   pval.size=3.5)
```
## Cam_90
```{r}
OS = read.table("~/Desktop/Melanoma/SurvivalResults_Cam_90_OS_Weighted_0.33_3.tsv", sep = "\t", header = TRUE, quote = "")
OS = OS[c("Signature", 
          "Signature + Sex + Age + as.character(Stage) + ECOG + treatment + as.numeric(Nclass)",
          "Signature + Sex + Age + as.character(Stage) + ECOG + treatment + as.numeric(Nclass) + TIL count"), ]
OS$Group = c("Cam_90", 
             "Cam_90+Sex+Age+Stage+\nECOG+treatment+Nclass",
             "Cam_90+Sex+Age+Stage+\nECOG+treatment+Nclass+\nTIL count")
OS$Event = c("OS")

pfs = read.table("~/Desktop/Melanoma/SurvivalResults_Cam_90_PFS_Weighted_0.33_3.tsv", sep = "\t", header = TRUE, quote = "")
pfs = pfs[c("Signature", 
          "Signature + Sex + Age + as.character(Stage) + ECOG + treatment + as.numeric(Nclass)",
          "Signature + Sex + Age + as.character(Stage) + ECOG + treatment + as.numeric(Nclass) + TIL count"), ]
pfs$Group = c("Cam_90", 
             "Cam_90+Sex+Age+Stage+\nECOG+treatment+Nclass",
             "Cam_90+Sex+Age+Stage+\nECOG+treatment+Nclass+\nTIL count")
pfs$Event = c("PFS")

df = rbind(OS, pfs)
df$Group = as.factor(df$Group)
df$Group = factor(df$Group, levels = rev(levels(df$Group)))
df$Event = as.factor(df$Event)

g3 <- ggplot(data=df,
       aes(x = Group,y = as.numeric(HazardRatio), ymin = as.numeric(Lower_HazardRatio), ymax = as.numeric(Upper_HazardRatio), 
           color = Event,
           label = paste("p=",p.value, sep = "")))+
    geom_pointrange(position=position_dodge(width=0.5))+
    geom_hline(yintercept =1, linetype=2)+
    xlab('')+
    ylab("Hazard Ratio (95% Confidence Interval)")+
    geom_errorbar(aes(ymin=as.numeric(Lower_HazardRatio), ymax=as.numeric(Upper_HazardRatio)),width=0.1,cex=1, position=position_dodge(width=0.5))+ 
    geom_text(hjust = -.05, vjust=-1, position=position_dodge(width=0.5))+
    #scale_y_continuous()+
    ylim(c(0,4))+
    scale_color_brewer(type = "qual", palette = "Set2")+
    coord_flip()+
    theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))
   
#ggarrange(g1, g2, align = "h", ncol = 1, nrow = 2, heights = c(4, 4))
ggsave(plot = g3, filename = "Cam_121_OS.png", device = "png", width = 16, units = "cm")
```

## Published signatures
```{r}
os = read.table("~/Desktop/Melanoma/SurvivalResults_Gerami_genes_OS_High_median_3.tsv", sep = "\t", header = TRUE, quote = "")
os = os[7:nrow(os),]
os = os[-2,]
os$Group = c("Decision-Dx", 
             "Decision-Dx+Sex", 
             "Decision-Dx+Age", 
             "Decision-Dx+Stage", 
             "Decision-Dx+ECOG", 
             "Decision-Dx+Treatment", 
             "Decision-Dx+Nclass",
             "Decision-Dx+Sex+Age+Stage+\nECOG+treatment+Nclass",
             "Decision-Dx+Sex+Age+Stage+\nECOG+treatment+Nclass+\nTIL count")
os$Event = c("OS")

pfs = read.table("~/Desktop/Melanoma/SurvivalResults_Gerami_genes_PFS_High_median_3.tsv", sep = "\t", header = TRUE, quote = "")
pfs = pfs[7:nrow(pfs), ]
pfs = pfs[-2, ]
pfs$Group = c("Decision-Dx", 
             "Decision-Dx+Sex", 
             "Decision-Dx+Age", 
             "Decision-Dx+Stage", 
             "Decision-Dx+ECOG", 
             "Decision-Dx+Treatment", 
             "Decision-Dx+Nclass",
             "Decision-Dx+Sex+Age+Stage+\nECOG+treatment+Nclass",
             "Decision-Dx+Sex+Age+Stage+\nECOG+treatment+Nclass+\nTIL count")
pfs$Event = c("PFS")

df = rbind(os, pfs)
df$Group = as.factor(df$Group)
df$Group = factor(df$Group, levels = c("Decision-Dx+Sex+Age+Stage+\nECOG+treatment+Nclass+\nTIL count","Decision-Dx+Sex+Age+Stage+\nECOG+treatment+Nclass", "Decision-Dx+Treatment","Decision-Dx+Stage","Decision-Dx+Sex","Decision-Dx+ECOG","Decision-Dx+Age","Decision-Dx+Nclass","Decision-Dx"))
df$Event = as.factor(df$Event)

g4 <- ggplot(data=df,
       aes(x = Group,y = as.numeric(HazardRatio), ymin = as.numeric(Lower_HazardRatio), ymax = as.numeric(Upper_HazardRatio), 
           color = Event,
           label = paste("p=",p.value, sep = "")))+
    geom_pointrange(position=position_dodge(width=0.5))+
    geom_hline(yintercept =1, linetype=2)+
    xlab('')+
    ylab("Hazard Ratio (95% Confidence Interval)")+
    geom_errorbar(aes(ymin=as.numeric(Lower_HazardRatio), ymax=as.numeric(Upper_HazardRatio)),width=0.1,cex=1, position=position_dodge(width=0.5))+ 
    geom_text(hjust = -.05, vjust=-1, position=position_dodge(width=0.5))+
    #scale_y_continuous()+
    ylim(c(0,2))+
    scale_color_brewer(type = "qual", palette = "Set2")+
    coord_flip()+
    theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))
   
#ggarrange(g1, g2, align = "h", ncol = 1, nrow = 2, heights = c(4, 4))
ggsave(plot = g4, filename = "Gerami_OS.png", device = "png", width = 16, units = "cm")

```

```{r}
os = read.table("~/Desktop/Melanoma/SurvivalResults_LMC_150_genes_OS_High_median_3.tsv", sep = "\t", header = TRUE, quote = "")
os = os[7:nrow(os),]
os = os[-2,]
os$Group = c("LMC_150", 
             "LMC_150+Sex", 
             "LMC_150+Age", 
             "LMC_150+Stage", 
             "LMC_150+ECOG", 
             "LMC_150+Treatment", 
             "LMC_150+Nclass",
             "LMC_150+Sex+Age+Stage+\nECOG+treatment+Nclass",
             "LMC_150+Sex+Age+Stage+\nECOG+treatment+Nclass+\nTIL count")
os$Event = c("OS")

pfs = read.table("~/Desktop/Melanoma/SurvivalResults_LMC_150_genes_PFS_High_median_3.tsv", sep = "\t", header = TRUE, quote = "")
pfs = pfs[7:nrow(pfs), ]
pfs = pfs[-2, ]
pfs$Group = c("LMC_150", 
             "LMC_150+Sex", 
             "LMC_150+Age", 
             "LMC_150+Stage", 
             "LMC_150+ECOG", 
             "LMC_150+Treatment", 
             "LMC_150+Nclass",
             "LMC_150+Sex+Age+Stage+\nECOG+treatment+Nclass",
             "LMC_150+Sex+Age+Stage+\nECOG+treatment+Nclass+\nTIL count")
pfs$Event = c("PFS")

df = rbind(os, pfs)
df$Group = as.factor(df$Group)
df$Group = factor(df$Group, levels = c("LMC_150+Sex+Age+Stage+\nECOG+treatment+Nclass+\nTIL count","LMC_150+Sex+Age+Stage+\nECOG+treatment+Nclass", "LMC_150+Treatment","LMC_150+Stage","LMC_150+Sex","LMC_150+ECOG","LMC_150+Age","LMC_150+Nclass","LMC_150"))
df$Event = as.factor(df$Event)

g5 <- ggplot(data=df,
       aes(x = Group,y = as.numeric(HazardRatio), ymin = as.numeric(Lower_HazardRatio), ymax = as.numeric(Upper_HazardRatio), 
           color = Event,
           label = paste("p=",p.value, sep = "")))+
    geom_pointrange(position=position_dodge(width=0.5))+
    geom_hline(yintercept =1, linetype=2)+
    xlab('')+
    ylab("Hazard Ratio (95% Confidence Interval)")+
    geom_errorbar(aes(ymin=as.numeric(Lower_HazardRatio), ymax=as.numeric(Upper_HazardRatio)),width=0.1,cex=1, position=position_dodge(width=0.5))+ 
    geom_text(hjust = -.05, vjust=-1, position=position_dodge(width=0.5))+
    #scale_y_continuous()+
    ylim(c(0,2))+
    scale_color_brewer(type = "qual", palette = "Set2")+
    coord_flip()+
    theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))
   
#ggarrange(g1, g2, align = "h", ncol = 1, nrow = 2, heights = c(4, 4))
ggsave(plot = g5, filename = "Gerami_OS.png", device = "png", width = 16, units = "cm")

```
```{r}
ggarrange(g4, g5, ncol = 1, nrow = 2, align = "v", common.legend = TRUE,
          heights = c(1, 1), labels = c("A", "B"))
ggsave("PubSigSurv.png", width = 16, height = 16, units = "cm", device = "png")
```
## LN

Downloaded from https://drive.google.com/drive/folders/1O-VhXpxhDZUo5_uG-Zz7bV6Lq8usUF8j

```{r}
os = read.table("~/Downloads/SurvivalResults_Signature_overlap_DASLarray_genes_OS_Weighted_median_3-2.txt", sep = "\t", header = TRUE, quote = "")
os = os[7:nrow(os),]
#os = os[-2,]
os$Group = c("Cam_121", 
             "Cam_121+Sex", 
             "Cam_121+Age", 
             "Cam_121+Stage", 
             "Cam_121+ECOG", 
             "Cam_121+Treatment", 
             "Cam_121+Nclass",
             "Cam_121+Sex+Age+Stage+\nECOG+treatment+Nclass")
os$Event = c("OS")

pfs = read.table("~/Downloads/SurvivalResults_Signature_overlap_DASLarray_genes_PFS_Weighted_median_3.txt", sep = "\t", header = TRUE, quote = "")
pfs = pfs[7:nrow(pfs), ]
#pfs = pfs[-2, ]
pfs$Group = c("Cam_121", 
             "Cam_121+Sex", 
             "Cam_121+Age", 
             "Cam_121+Stage", 
             "Cam_121+ECOG", 
             "Cam_121+Treatment", 
             "Cam_121+Nclass",
             "Cam_121+Sex+Age+Stage+\nECOG+treatment+Nclass")
pfs$Event = c("PFS")

df = rbind(os, pfs)
df$Group = as.factor(df$Group)
df$Group = factor(df$Group, levels = c("Cam_121+Sex+Age+Stage+\nECOG+treatment+Nclass", "Cam_121+Treatment","Cam_121+Stage","Cam_121+Sex","Cam_121+ECOG","Cam_121+Age","Cam_121+Nclass","Cam_121"))
df$Event = as.factor(df$Event)

g6 <- ggplot(data=df,
       aes(x = Group,y = as.numeric(Hazard_Ratio), ymin = as.numeric(Lower_HazardRatio), ymax = as.numeric(Upper_HazardRatio), 
           color = Event,
           label = paste("p=",p_value, sep = "")))+
    geom_pointrange(position=position_dodge(width=0.5))+
    geom_hline(yintercept =1, linetype=2)+
    xlab('')+
    ylab("Hazard Ratio (95% Confidence Interval)")+
    geom_errorbar(aes(ymin=as.numeric(Lower_HazardRatio), ymax=as.numeric(Upper_HazardRatio)),width=0.1,cex=1, position=position_dodge(width=0.5))+ 
    geom_text(hjust = -.05, vjust=-1, position=position_dodge(width=0.5))+
    #scale_y_continuous()+
    ylim(c(0,4))+
    scale_color_brewer(type = "qual", palette = "Set2")+
    coord_flip()+
    theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))
   
#ggarrange(g1, g2, align = "h", ncol = 1, nrow = 2, heights = c(4, 4))
ggsave(plot = g6, filename = "Cam_121_Ln_OS.png", device = "png", width = 16, height = 12, units = "cm")

```
