---
title: "AVAST-M_TILCounts"
author: "Manik Garg"
date: "29/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("ggplot2")
theme_set(ggpubr::theme_pubr(base_size=10, legend='bottom'))
```

```{r}
library(openxlsx)
```

```{r}
#jt = read.xlsx("~/Downloads/AVAST-M_primaries_TILCountData_JT.xlsx")
#ns = read.xlsx("~/Downloads/Scores_NS_V2.xlsx")
jt_ns_sm_scores = read.table("~/Downloads/JT_NS_SM_Combined.txt", sep = "\t", header = TRUE, quote = "")
```

```{r}
# nsScores = ns[!(is.na(ns$ABSENT)) | !(is.na(ns$`NON-BRISK.LymP.in.tumour`)) | !(is.na(ns$BRISK)), 
#               c("Cases", "ABSENT", "NON-BRISK.LymP.in.tumour", "BRISK", "TIL.GRADE", "Additional.comments", "Density", "Distribution")]
# colnames(nsScores) = paste("NS", colnames(nsScores), sep = "_")
```

```{r}
# jtScores = jt[!(is.na(jt$Clark_score)), 
#               c("RNASeq_sampleID", "Scanned_filename", "Comments_scan", "Clark_score", "TIL_grade", "Comments", "Density", "Distribution", "Scanning_batch")]
# colnames(jtScores) = paste("JT", colnames(jtScores), sep = "_")
```

```{r}
# combinedScores = merge(jtScores, y = nsScores, by.x = "JT_Scanned_filename",
#                        by.y = "NS_Cases")
```

Remove scans labelled as having poor quality by JT and NS
```{r}
# combinedScoresSub = combinedScores[-grep("v poor", combinedScores$JT_Comments, ignore.case = TRUE), ]
# combinedScoresSub = combinedScoresSub[-grep("too poor", combinedScoresSub$JT_Comments, ignore.case = TRUE), ]
# combinedScoresSub = combinedScoresSub[-grep("too faded", combinedScoresSub$JT_Comments, ignore.case = TRUE), ]
# combinedScoresSub = combinedScoresSub[-grep("Dermal deposit", combinedScoresSub$NS_Additional.comments, ignore.case = FALSE), ]
```

```{r}
# combinedScoresSub$NS_Clark_score = combinedScoresSub$JT_Clark_score
# combinedScoresSub$NS_Clark_score[combinedScoresSub$NS_ABSENT == "x"] = 0
# combinedScoresSub$NS_Clark_score[combinedScoresSub$`NS_NON-BRISK.LymP.in.tumour` == "x"] = 1
# combinedScoresSub$NS_Clark_score[combinedScoresSub$NS_BRISK == "x"] = 2
```

```{r}
# rearrangeColumns = combinedScoresSub[, c("JT_RNASeq_sampleID", 
#                                          "JT_Scanned_filename",
#                                          "JT_Scanning_batch",
#                                          "JT_Clark_score",
#                                          "NS_Clark_score",
#                                          "NS_ABSENT", 
#                                          "NS_NON-BRISK.LymP.in.tumour", 
#                                          "NS_BRISK", 
#                                          "JT_Density",
#                                          "NS_Density",
#                                          "JT_Distribution",
#                                          "NS_Distribution",
#                                          "JT_TIL_grade",
#                                          "NS_TIL.GRADE",
#                                          "JT_Comments_scan",
#                                          "JT_Comments",
#                                          "NS_Additional.comments")]
```

```{r}
#write.xlsx(rearrangeColumns, file="./combined_scores_V2.xlsx")
```

## Plotting TIL counts for AVAST-M data

```{r}
# tilCount = jtScores[, c("JT_RNASeq_sampleID", "JT_Clark_score", "JT_TIL_grade")]
# cam_121 = data.frame("Cam_121" = reducedGeneSignature, "Sample" = names(reducedGeneSignature))
# tilCount = merge(tilCount, cam_121, by.x = "JT_RNASeq_sampleID", by.y = "Sample")
```

```{r}
# my_comparisons <- list( c("absent", "nonbrisk"), c("nonbrisk", "brisk"), c("absent", "brisk") )
# tilCount$JT_Clark_score <- as.factor(tilCount$JT_Clark_score)
# levels(tilCount$JT_Clark_score) <- c("absent", "nonbrisk", "brisk")
# #tilCount$JT_Clark_score <- factor(tilCount$JT_Clark_score, levels = c("absent", "nonbrisk", "brisk"))
# ggplot(tilCount, aes(x=JT_Clark_score, y=Cam_121, fill = JT_Clark_score))+
#   geom_violin()+
#   scale_fill_brewer(type="qual", palette = "Dark2", name = "Clark score")+
#   xlab("Clark score")+
#   ylab("Weighted Cam_121 score (standardized)")+
#   geom_hline(yintercept = -0.38, color = "grey", linetype = "longdash")+
#   ggpubr::stat_compare_means(comparisons = my_comparisons, method = "t.test")+ # Add pairwise comparisons p-value
#   ggpubr::stat_compare_means(label.y = 6, method = "anova")     # Add global p-value
# ggsave("Cam_121_ClarkScore_AVAST-M.png", device = "png", width = 8, units = "cm")
```

```{r}
# my_comparisons <- list( c("0", "1"), c("1", "2"), c("2", "3") )
# tilCount$JT_TIL_grade <- as.factor(tilCount$JT_TIL_grade)
# ggplot(tilCount, aes(x=JT_TIL_grade, y=Cam_121, fill = JT_TIL_grade))+
#   geom_violin()+
#   scale_fill_brewer(type="qual", palette = "Dark2", name = "MIA score")+
#   xlab("MIA score")+
#   ylab("Weighted Cam_121 score (standardized)")+
#   geom_hline(yintercept = -0.38, color = "grey", linetype = "longdash")+
#   ggpubr::stat_compare_means(comparisons = my_comparisons, method = "t.test")+ # Add pairwise comparisons p-value
#   ggpubr::stat_compare_means(label.y = 6, method = "anova")     # Add global p-value
# ggsave("Cam_121_MIAScore_AVAST-M.png", device = "png", units = "cm", width = 8)
```
## Plotting TIL counts for Leeds data

```{r}
# tilCountFile = read.table("~/Downloads/ROY_Sanger/cam121tils.txt", sep = "\t", header = TRUE, quote = "")
```
Converting back to the original sign
```{r}
#tilCountFile$cam121score = -tilCountFile$cam121score
```
Removing the samples for which there is no til information
```{r}
#tilCountFile = tilCountFile[!(tilCountFile$tils==""),]
```

Make violin plot with p-values on the top
```{r}
# my_comparisons <- list( c("absent", "nonbrisk"), c("brisk", "nonbrisk"), c("absent", "brisk") )
# tilCountFile$tils <- factor(tilCountFile$tils, levels = c("absent", "nonbrisk", "brisk"))
# ggplot(tilCountFile, aes(x=tils, y=cam121score, fill = tils))+
#   geom_violin()+
#   scale_fill_brewer(type="qual", palette = "Dark2", name = "Clark score")+
#   xlab("Clark Score")+
#   ylab("Weighted Cam_121 score (standardized)")+
#   geom_hline(yintercept = -0.38, color = "grey", linetype = "longdash")+
#   ggpubr::stat_compare_means(comparisons = my_comparisons, method = "t.test")+ # Add pairwise comparisons p-value
#   ggpubr::stat_compare_means(label.y = 6, method = "anova")     # Add global p-value
# ggsave("Cam_121_ClarkScore_Leeds.png", device = "png", width = 0.8, units = "cm")
```

```{r}
combinedScore = data.frame("Scanned_file.me"= jt_ns_sm_scores$JT_Scanned_file.me, 
                                "R.Seq_sampleID"= jt_ns_sm_scores$JT_R.Seq_sampleID, 
                                "ClarkScore"= ifelse(jt_ns_sm_scores$JT_Clark_score==jt_ns_sm_scores$NS_Clark_score,
                            jt_ns_sm_scores$JT_Clark_score, 
                            jt_ns_sm_scores$SM_Clark_score),
                           "MIAScore"= ifelse(jt_ns_sm_scores$JT_TIL_grade==jt_ns_sm_scores$NS_TIL.GRADE,
                            jt_ns_sm_scores$JT_TIL_grade, 
                            jt_ns_sm_scores$SM_TIL_grade))

```

```{r}
cam_121 = read.table("~/Desktop/Melanoma//Cam_121_AvastM_Skin.tsv", sep = "\t", header = TRUE, quote = "")
cam_121$Sample = rownames(cam_121)
tilCount = merge(combinedScore, cam_121, by.x = "R.Seq_sampleID", by.y = "Sample")
```

```{r}
my_comparisons <- list( c("absent", "nonbrisk"), c("nonbrisk", "brisk"), c("absent", "brisk") )
tilCount$ClarkScore <- as.factor(tilCount$ClarkScore)
levels(tilCount$ClarkScore) <- c("absent", "nonbrisk", "brisk")
#tilCount$JT_Clark_score <- factor(tilCount$JT_Clark_score, levels = c("absent", "nonbrisk", "brisk"))
g1<- ggplot(tilCount[!is.na(tilCount$ClarkScore), ], aes(x=ClarkScore, y=Signature))+
  geom_violin()+
  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  #scale_fill_brewer(type="qual", palette = "Dark2", name = "Cam_121 risk group")+
  xlab("Clark score (AVAST-M Skin)")+
  ylab("Weighted Cam_121 score (stand.)")+
  geom_hline(yintercept = quantile(tilCount$Signature, 0.33), color = "grey", linetype = "longdash")+
  ggpubr::stat_compare_means(comparisons = my_comparisons, method = "t.test")+ # Add pairwise comparisons p-value
  ggpubr::stat_compare_means(label.y = 6, method = "anova")     # Add global p-value
ggsave("Cam_121_ClarkScore_AVAST-M.png", device = "png", width = 8, units = "cm")
```
```{r}
my_comparisons <- list( c("0", "1"), c("1", "2"), c("2", "3") )
tilCount$MIAScore <- as.factor(tilCount$MIAScore)
g2<- ggplot(tilCount[!is.na(tilCount$MIAScore), ], aes(x=MIAScore, y=Signature))+
  geom_violin()+
  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  scale_fill_brewer(type="qual", palette = "Dark2", name = "MIA score")+
  xlab("MIA score (AVAST-M Skin)")+
  ylab("Weighted Cam_121 score (stand.)")+
  geom_hline(yintercept = quantile(tilCount$Signature, 0.33), color = "grey", linetype = "longdash")+
  ggpubr::stat_compare_means(comparisons = my_comparisons, method = "t.test")+ # Add pairwise comparisons p-value
  ggpubr::stat_compare_means(label.y = 6, method = "anova")     # Add global p-value
ggsave("Cam_121_MIAScore_AVAST-M.png", device = "png", units = "cm", width = 8)

```
```{r}
g2
```

```{r}
#write.table(tilCount, file = "./AVAST-M_TILCount.tsv", sep = "\t", col.names = TRUE, row.names = FALSE, quote = FALSE)

write.xlsx(tilCount, "~/Desktop/Melanoma/githubUpload/Source_Data/Figs_5A_5C.xlsx", colNames = TRUE, rowNames = TRUE, append = TRUE)

```

## Plotting TIL counts for Leeds data

```{r}
tilCountFile = read.table("~/Downloads/ROY_Sanger/cam121tils.txt", sep = "\t", header = TRUE, quote = "")
```
Converting back to the original sign
```{r}
tilCountFile$cam121score = -tilCountFile$cam121score
```
Removing the samples for which there is no til information
```{r}
tilCountFile = tilCountFile[!(tilCountFile$tils==""),]
```

Make violin plot with p-values on the top
```{r}
my_comparisons <- list( c("absent", "nonbrisk"), c("brisk", "nonbrisk"), c("absent", "brisk") )
tilCountFile$tils <- factor(tilCountFile$tils, levels = c("absent", "nonbrisk", "brisk"))
g3<-ggplot(tilCountFile, aes(x=tils, y=cam121score))+
  geom_violin()+
  geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  scale_fill_brewer(type="qual", palette = "Dark2", name = "Clark score")+
  xlab("Clark Score (LMC)")+
  ylab("Weighted Cam_121 score (stand.)")+
  geom_hline(yintercept = -0.38, color = "grey", linetype = "longdash")+
  ggpubr::stat_compare_means(comparisons = my_comparisons, method = "t.test")+ # Add pairwise comparisons p-value
  ggpubr::stat_compare_means(label.y = 6, method = "anova")     # Add global p-value
ggsave("Cam_121_ClarkScore_Leeds.png", device = "png", width = 8, units = "cm")
```
```{r}
g3
```
```{r}
ggpubr::ggarrange(g1, g3, g2, labels = c("A", "B", "C"), ncol = 2, nrow = 2, hjust = c(0.1, 0.1, 0.1))
ggsave("Cam_121_TILCount.pdf", device = "pdf", units='cm', width = 16, height = 16)
ggsave("Cam_121_TILCount.png", device = "png", units='cm', width = 16, height = 16 )
```

```{r}
#write.table(tilCount, file = "./AVAST-M_TILCount.tsv", sep = "\t", col.names = TRUE, row.names = FALSE, quote = FALSE)

write.xlsx(tilCountFile, "~/Desktop/Melanoma/githubUpload/Source_Data/Figs_5B.xlsx", colNames = TRUE, rowNames = TRUE, append = TRUE)

```